% Appendix Template

\chapter{Publications et communications} % Main appendix title

\label{Annexes2} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\lhead{Annexes 2. \emph{Publications}} % Change X to a consecutive letter; this is for the header on each page - perhaps a shortened title

\section{Publications}
	\subsection{Articles dans des revues à comité de lecture}
\textbf{Boulay, J.}, Hédouin, V. and Charabidzé, D. Submitted. Mixed-species aggregation in arthropods - a review. \textit{Behavioral Ecology}.

Aubernon, C., \textbf{Boulay, J.}, Hédouin, V. and Charabidzé, D. Submitted. Thermoregulation in gregarious Dipteran larvae: evidence of species-specific temperature selection. \textit{Entomologia Experimentalis et Applicata}.

\textbf{Boulay, J.}, Deneubourg, J.-L., Hédouin, V. and Charabidzé, D. Resubmitted. Interspecific shared collective decision-making in two forensically important species. \textit{Proceedings of the Royal Society of London B}.

\textbf{Boulay, J.}, Betremieux, C., Hédouin, V. and Charabidzé, D. 2015. A first insight in the scanning behaviour of presocial blow fly larvae. \textit{Physiological Entomology}, DOI: 10.1111/phen.12117 (B journal, IF 1.416).

\textbf{Boulay, J.}, Devigne, C., Gosset, D. and Charabidzé, D. 2013. Evidence of active aggregation behaviour in \textit{Lucilia sericata} larvae and possible implication of a conspecific mark. \textit{Animal Behaviour}, 85, 1191-1197 (B journal, IF 3.137).

\textbf{Boulay, J.}, Chaillou, E., Bertin, A., Constantin, P., Arnould, C., Leterrier, C. and Calandreau, L. 2013. A higher inherent trait for fearfulness is associated with increased anxiety-like behaviours and diazepam sensitivity in Japanese quail. \textit{Behavioural Brain Research}, 237, 124-128 (B journal, IF 3.028).


	\subsection{Chapitre de livre}
Aubernon, C., \textbf{Boulay, J.} et Charabidzé, D. 2014. Comportement et développement des larves nécrophages. Dans : \textit{Insectes, cadavre et scène de crime : Principes et applications de l’entomologie médico-légale}, Charabidzé et Gosselin (eds), De Boeck édition.


\section{Communications dans des colloques internationaux}

	\subsection{Communications orales}

\textbf{Boulay, J.}, Charabidzé, D. and Hédouin, V. 2014. Aggregation of Diptera larvae on homogenous and patchy environment. \textit{11th meeting of EAFE}, Lille, France.

\textbf{Boulay, J.}, Devigne, C., Verheggen, F., Lognay, G. and Hédouin, V. 2013. Aggregation behaviour of necrophagous dipteran larvae: what do we know and where are we? \textit{9th Ecology and Behaviour meeting}, Strasbourg, France.

\textbf{Boulay, J.}, Charabidzé, D., Devigne, C. and Hédouin, V. 2011. Effect of different signals on the gregarious behavior of carrion fly larvae (\textit{Lucilia sericata}). \textit{7th Ecology and Behaviour meeting}, Rennes, France.
    
    \subsection{Communications affichées}
    
Delannoy, Y., Colard, T., Aubernon, C., \textbf{Boulay, J.}, Hédouin, V. and Gosset, D. 2015. The effects of soil environment on bone mass: a human prospective taphonomic study. \textit{AAFS 2015}, Orlando, USA.

\textbf{Boulay, J.}, Charabidzé, D., Devigne, C., Deneubourg, J.-L. and Hédouin, V. 2013. Aggregation of Diptera larvae on homogenous and patchy environment. \textit{Behaviour 2013}, Newcastle, UK.



\section{Communications dans des colloques nationaux}

	\subsection{Communications orales}
Charabidzé, D., \textbf{Boulay, J.}, Aubernon, C., Devigne, C. et Hédouin, V. 2013. Stratégies thermiques des larves nécrophages. \textit{Colloque de Biologie de l’Insecte}, Montpellier, France.

\textbf{Boulay, J.}, Charabidzé, D., Hédouin, V. et Gosset, D. 2012. Présence de Dermestes sp. sur les corps découverts en intérieur : états des connaissances et objectifs de recherche. \textit{12\up{ème} Congrès d’Anthropologie médico-légale}, Nice, France.

\textbf{Boulay, J.}, Aubernon, C., Charabidzé, D., Hédouin, V. et Gosset, D. 2011. Les analyses complémentaires : l’entomologie médico-légale. \textit{Congrès de la Société Française de Médecine Légale}, Rouen, France.

    \subsection{Communications affichées}
\textbf{Boulay, J.}, Charabidzé, D., Devigne, C., Deneubourg, J.-L. et Gosset, D. 2012. Plus odorant qu’un cadavre en décomposition ? Preuves d’un signal conspécifique impliqué dans l’agrégation des larves nécrophages de \textit{Lucilia sericata} (Diptera : Calliphoridae). \textit{Colloque de la Société Française pour l’Étude du Comportement Animal, Le comportement animal : questions proximales et évolutives}. St-Étienne, France.    
    
    
    
\section{Activité de vulgarisation}

\textbf{Boulay, J.} et Broly, P. 2014. Le grégarisme chez les insectes. \textit{Espèces}, n\up{o}10.

Aubernon, C., \textbf{Boulay, J.}, Charabidzé, D. et Gosselin, M. 2012. Quand l’entomologiste devient expert : les insectes nécrophages et la datation du décès. \textit{Espèces}, n\up{o}5.

\textit{Ma thèse en 2min}. Websérie du Huffington Post. 22/11/2014. 

\textit{Les pieds sur Terre}. Radio France Bleu Frequenza Mora. 4/11/2012.

Animation de stand lors de \textit{la Fête de la Science}. 2014, 2015.

\section{Bourses}

Bourse de l'EDBSL (École Doctorale Biologie-Santé de Lille). 450\euro, 2015.

Bourse de la SFECA (Société Française pour l'Étude du Comportement Animal). 250\euro, 2013. 


\clearpage